Manifold Clustering in the Setting of Generalized Random Dot Product Graphs

### 2023-05-24 sdss-2023/slides.Rmd
minor changes
minor updates

# gridExtra::grid.arrange(latent.vecs, rdpg, ase, nrow = 1)
gridExtra::grid.arrange(latent.vecs, rdpg, nrow = 1)
```

@@

where $\hat{x}_i$ are the embedding vectors of $A$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then as $n \to \infty$, $K$-curves clustering outputs estimates such that

>>>>

gridExtra::grid.arrange(latent.vecs, rdpg, ase, nrow = 1)
# gridExtra::grid.arrange(latent.vecs, rdpg, nrow = 1)
```

@@

where $\hat{x}_i$ are the embedding vectors of $A$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then as $n \to \infty$, $K$-curves clustering outputs estimators such that
